### 2022-07-27 paper/akweury/document.tex
update eval

We evaluate the GCNN architecture based light net on the test dataset. The light net parameters are further used as the initial parameter of light branch of the Trignet.

>>>>

For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net that introduced in \ref{sec:trip-net}. 
The qualitative evaluation is shown in figure \ref{fig:trip-eval}. As a comparison, we create a similar model, which keeps the vertex and light pipes same but replace the image pipe with standard convolution layers (corresponding "AN" model in the figures and tables).

The quantitative evaluation is shown in figure \ref{fig:trip-scatter}.
We evaluate the GCNN architecture based light net on the test dataset. The light net parameters are further used as the initial parameter of light branch of the Trignet.
